---
title: "Statistical Concepts"
---

# Assignments  

## Expected value, variance and standard deviation

```{r}

library(tidyverse)
random_vars <- readRDS("D:/GitHub/cdsba-pamoviedo/Causal_Data_Science_Data/random_vars.rds")

# Compute the expected value, variance and standard deviation for variable age
mean_age <- mean(random_vars$age)
mean_age
var_age <- var(random_vars$age)
var_age
sd_age <- sd(random_vars$age)
sd_age

#Compute the expected value, variance and standard deviation for variable income
mean_income <- mean(random_vars$income)
mean_income
var_income <- var(random_vars$income)
var_income
sd_income <- sd(random_vars$income)
sd_income

```

### Results 
*  Age expected value: 33.471  
*  Age variance: 340.6078  
*  Age standard deviation: 18.45556  

*  Income expected value: 3510.731  
*  Income variance: 8625646
*  Income standard deviation: 2936.945

## Does it make sense to compare standard deviations?  

*  It doesn't make sense to compare them since they are individual data sets and the comparison would give us no insight.

## Compute covariance and correlation 

```{r}

#Compute the covariance and correlation between both variables
covariance <- cov(random_vars$age,random_vars$income)
covariance
correlation <- cor(random_vars$age,random_vars$income)
correlation

```

### Results
*  Covariance: 29700.15  
*  Correlation: 0.5479432

## What measure is easier to interpret?  
*  Covariance indicates the direction of the linear relationship between variables but it doesn't provide a standardized measure.  
*  Correlation is a standardized measure that ranges between -1 and 1. With -1 indicating a perfect negative linear relationship, 0 indicating no linear relationship and 1 indicating a perfect positive linear relationship.  

*  With the description above, it is easier to interpret the correlation since the values are fixed and we know that the 0.5479 represents a strong linear relation because it is closer to 1. The covariance value since it has no standardized measure, we are unable to know if it is representing a high or low value.  

## Compute the conditional expected value for 

1.  $E[income|age<=18]$  
2.  $E[income|age\in[18,65)]$
3.  $E[income|age>=65]$  

```{r}
cev1<- filter(random_vars,age<=18)
mean_cev1 <- mean(cev1$income)
mean_cev1
cev2<- filter(random_vars,age>=18&age<65)
mean_cev2 <- mean(cev2$income)
mean_cev2
cev3<- filter(random_vars,age>=65)
mean_cev3<- mean(cev3$income)
mean_cev3
```

### Results 

1.  $E[income|age<=18]= 389.6074$  
2.  $E[income|age\in[18,65)]=4685.734$
3.  $E[income|age>=65]=1777.237$  

