---
title: "Regression and Statistical Inference"
---
# Assignments  

## Read the data and check the dimensions

```{r}

library(tidyverse)
car <- readRDS("D:/GitHub/cdsba-pamoviedo/Causal_Data_Science_Data/car_prices.rds")
dim_car <- dim(car)

``` 

1.  How many rows does the data have: 181  
2.  How many columns does the data have: 22  

## Get a more detailed look at the data
### What data types do you see? 
### How do numbers differ from strings regarding their data type?  

 
```{r}
glimpse(car)
```
 
Using the "glimpse()" command we got a more detailed look at the data which consists of numbers and characters.
Numbers are represented as numeric values while strings are sequences of characters.

## Run a linear regression  
```{r}
lm_all<- lm(price~., data = car)
summary(lm_all)
```
Looking at the summary from the linear regression, those factors that have a *** next to the p value represent the significance, so we will take those as relevant for pricing a car. 
The factors are the following: 

*  Engine Type  
*  Engine Size  
*  Peak RPM  
*  Stroke


## Chose one regressor 

```{r}
lm_imp<- lm(price~enginetype+enginesize+peakrpm+stroke, data=car)
summary(lm_imp)
```
With the code above we can see that the most relevant factor out of all was "engine size" since it has the smallest P-value and its the regressor we will use.

### 1. explain what data type it is and what values it can take on  

```{r}
min(car$enginesize)
max(car$enginesize)
```

*  From the glimpse we know that the data type for "engine size" is a double. 
*  The values it can take on we use the min and max functions to know the range of the "engine size". From 61-326. 

### 2. what effect it has on the price and what changing the value would have as a result  
*  Since engine size was the most significant factor, having the lowest p value, which means the price is dependent on it and changing the value would affect the price, when the engine size increases, the price will increase as well. 

### 3. whether its effect is statistically significant
*  A low p value provides support for the claim that the alternative hypothesis is true, which means there is a significant correlation between the variables.  

## Add a variable seat_heating, assign a value TRUE for all observations.   
### Assign it to a new object and run a regression.  
```{r}
ncar<- car %>% mutate(seat_heating = TRUE)
lm_final <- lm(price~., data=ncar)
summary(lm_final)
```
### What coefficient do you get for the new variable seat_heating and how can you explain it? 
*  The coefficient for the new variable is NA since we are using logical variables when the other data sets are numeric values
