---
title: "Difference-in-Differences"
---

#  Assignment 

*  Imagine, you are manager of a large health provider that manages many hospitals and you want to test how a new admission procedure affects patient satisfaction. You randomly selected 18 hospitals that introduced the new admission procedure and compare them to 28 other hospitals that did not introduce the method. For both groups of hospitals you collected data from before and after the introduction. The data you have collected is from patient surveys where they were asked how satisfied they are.

###  Load the data then perform a difference-in-differences analysis by:

##  Manually computing the mean satisfaction for treated and control hospitals before and after the treatment. 

```{r}

library(tidyverse)

#Load the data 
Hospitals <- readRDS("D:/GitHub/cdsba-pamoviedo/Causal_Data_Science_Data/hospdd.rds")

# Manually compute differences
# Step 1: Difference between treatment and control group BEFORE treatment
before_control_A <- Hospitals %>%
  filter(hospital >= 19 & hospital<= 46, procedure == 0) %>% 
  pull(satis)

before_treatment_A <- Hospitals %>%
  filter(hospital >= 1 & hospital<=18, procedure == 0) %>% 
  pull(satis)

diff_before_A <- before_treatment_A - before_control_A

# Step 2: Difference between treatment and control group AFTER treatment
after_control_A <- rep(0, dim(Hospitals)[1])

after_treatment_A <- Hospitals  %>%
  filter(hospital >= 1 & hospital<=18, procedure == 1) %>% 
  pull(satis)

diff_after_A <- after_treatment_A - after_control_A

# Step 3: Difference-in-differences.
diff_diff_A <- diff_after_A - diff_before_A
sprintf("Estimate: %.2f", diff_diff_A)

```

##  Using a linear regression to compute the estimate. Also, include group and time fixed effects in the regression. 

### month + hospital
```{r}
lm_mh <- lm(satis ~ month + hospital, data = Hospitals)
summary(lm_mh)
```

### as.factor(month) + as.factor(hospital)
```{r}
lm_factor <- lm(satis ~ as.factor(month) + as.factor(hospital), data = Hospitals)
summary(lm_factor)
```

### Explain the difference between both methods

*  month + hospital: treats months and hospitals as numeric variables and assumes a linear relationship between them. The coefficient estimation is separate for each month and hospital
*  as.factor treats the months and hospitals as factors which allows non-linear relationships. It estimates separate fixed effects for each month and hospital